Functory: A Distributed Computing Library \\ for Objective Caml \thanks{This research was partly supported by the French national project U3CAT (\emph{Unification of Critical C Code Analysis Techniques}, ANR-08-SEGI-021).}

### 2011-03-02 doc/tfp-2011/main.tex
updated (still incomplete) related work subsection [KK]

\paragraph{Related Work.}
Closest to the approach in this paper is Yohann Padioleau's MapReduce
implementation in \Ocaml~\cite{poor-man-mapreduce}.  It is built on
top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade
protocol for message passing.  Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a 
more generic API together with fault tolerance.  There are other
distributed computing libraries on top of which one could implement
the library discussed in this paper. \JoCaml~\cite{jocaml} is one of
them. However, \JoCaml\ does not provide fault tolerance, which is
indispensable in a distributed setting. The user has to include code
for fault tolerance, as already demonstrated in some \JoCaml\
experiments~\cite{mandel2008}.

>>>>

\paragraph{Related Work.}

There are several implementations of Google's Map/Reduce in functional
programming languages. But Functory was just inspired by Google's
Map/Reduce and is not exactly a Map/Reduce implementation. The
simplest difference comes from the very fact that Functory does not
operate on key/value pairs. In order to compare and distinguish
Functory from other work with related goals and motivations, we can
broadly classify the related work in this domain into:
\begin{enumerate}
\item Distributed Functional Languages (DFLs) - functional
  languages that provide built-in primitives for
  distribution. Examples include ML5, JoCaml, Glasgow Distributed
  Haskell, Erlang, etc.
\item Libraries for existing and well-known functional programming
  languages that could be used in order to relieve the user from
  implementing intricate details of distribution like
  fault-tolerance, socket programming, etc.
\end{enumerate}

\JoCaml\ is one of the DFLs which provides communication primitives
(like channels) for transmitting computations. On the other hand,
\JoCaml\ can not in a true sense be used as a distributed computing
library. It does not provide fault tolerance, which is indispensable
in a distributed setting. The user has to include code for fault
tolerance, as already demonstrated in some \JoCaml\
experiments~\cite{mandel2008}.

ML5~\cite{ML5}, a variant of ML, is a programming language for
distributed computing, specialized for web programming. It provides
primitives for transferring control between the client and the server,
as well as low-level primitives for marshalling the data. In
particular, it achieves type-safe marshalling. As in the case before,
ML5 is a programming language that offers primitives for code
mobility, rather than a user-friendly API for distribution of
computation and fault-tolerance.

Glasgow Distributed Haskell

The above mentioned languages are programming languages themselves,
our library, Functory, could be implemented using any of the above.

We now turn to distributed computing libraries for general purpose
functional languages and weed out the distinguishing features of
Functory from other similar libraries.

OcamlP3L

-----------  BELOW THIS IS THE OLD RELATED WORK --------

% -- BELOW HERE IS OLD RELATED-WORK

Closest to the approach in this paper is Yohann Padioleau's MapReduce
implementation in \Ocaml~\cite{poor-man-mapreduce}.  It is built on
top of OCamlMPI~\cite{ocamlMPI}, while our approach uses a homemade
protocol for message passing.  Currently, we have less flexibility
w.r.t. deployment of the user program than OCamlMPI; on the other
hand, we provide a 
more generic API together with fault tolerance.  There are other
distributed computing libraries on top of which one could implement
the library discussed in this paper. \JoCaml~\cite{jocaml} is one of
them. However, \JoCaml\ does not provide fault tolerance, which is
indispensable in a distributed setting. The user has to include code
for fault tolerance, as already demonstrated in some \JoCaml\
experiments~\cite{mandel2008}.
